### 2020-07-22 paper/methods.tex

The assessment of the optimal absorber radius should be an important consideration. If the CR radius is too large, the absorber material is not effectively utilized, due to self-shielding. We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the B$_4$C control rod. As shown in Figure~\ref{fig:Radius}, in the region between 0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius. However, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture.
From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.1-cm-thick gap between the 
cladding and guide tube to facilitate the control rod movement. However, absorber-cladding gap was neglected for simplicity.
All densities of rod materials are listed in
Table~\ref{tab:table111}.

@@

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}
In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
perform steady-state calculations for a full 3D model of the SD-TMSR with 
the suggested control rod design. We adopted the ENDF-VII.0 cross section library 
for all calculations in the present work. The results demonstrated in this study were obtained after full-core calculations simulating 25$\times$10$^6$ active neutron histories per cycle. Simulations consisted in 500 active cycles of 5$\times$10$^4$ neutrons subdivided in 8 parallel tasks. Each simulation skipped 50 inactive cycles before beginning active tallies to allow for the convergence of the fission source distribution. Convergence has been checked through the fission source entropy. The statistical error in $k_{eff}$ was $\leq$ $25$ $pcm$.

@@

The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation} and it accounts for the steady state of the fuel salt.

>>>>

The assessment of the optimal absorber radius should be an important consideration. If the CR radius is too large, the absorber material is not effectively utilized, due to self-shielding. We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the B$_4$C control rod. As shown in Figure~\ref{fig:Radius}, in the region between 0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius. However, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture.
From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.1-cm-thick gap between the 
cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity.
All densities of rod materials are listed in
Table~\ref{tab:table111}.

@@

\section{Methodology and tools} \label{Methodology-and-tools}
\subsection{Control rod design evaluation}
In this work, SERPENT-2 \cite{leppanen2014serpent} is used to 
perform steady-state calculations for a full 3D model of the SD-TMSR with 
the suggested control rod design. We adopted the ENDF/B-VII.0 \cite{CHADWICK20062931} cross section library 
for all calculations in the present work. The results demonstrated in this study were obtained after full-core calculations simulating 25$\times$10$^6$ active neutron histories per cycle. Simulations consisted in 500 active cycles of 5$\times$10$^4$ neutrons subdivided in 8 parallel tasks. Each simulation skipped 50 inactive cycles before beginning active tallies to allow for the convergence of the fission source distribution. Convergence has been checked through the fission source entropy. The statistical error in $k_{eff}$ was $\leq$ $25$ $pcm$.

@@

The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation}, and it accounts for the steady-state of the fuel salt.
